comgen-outline

### 2017-08-11 paper/comgen-paper.Rmd
wip

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in an open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just rare (e.g., understanding the properties of lightning).
It thus is crucial that language allow us to communicate such *generalizations* to each other.
By sharing painfully-won generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.

Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. [XXX cite older stuff. eg hume]
Cooperative teachers can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.

@@

[XXX first three pars are floppy. tighten.
There haven't been (many)? Formal models of generic language. Say why this is important.
To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
Then we need to say how these probabilities are communicated. Use RSA...]

>>>>

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in our open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding the properties of lightning).
It thus is crucial that language allow us to communicate such *generalizations* to each other.
By sharing generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.
Furthermore, sharing generalizations from one generation to the next may be a crucial mechanism behind the cultural ratchet \ndg{cite. or remove if you don't like it here}.

Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume}
Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.
\ndg{this par doesn't really do much}

@@

\ndg{prev three pars are floppy. tighten.
There haven't been (many?) formal models of generic language. Say why this is important.
To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
Then we need to say how these probabilities are communicated. Use RSA...}
